Open-Set Domain Adaptation through Self-Supervision

### 2022-02-13 paper/main.tex
center loss restatement

The approach presented in this paper combines the power of the self-supervised learning with the standard supervised learning approach for semantic class recognition.
We propose a two stage method aiming to identify and isolate unknown class samples in the first stage, 
and reducing the domain gap between domains in the second stage to avoid negative transfer.
This is done by using a modified version of the rotation task as self-supervised method,
predicting the relative rotation between an image and its rotated version.
Finally, a classifier is used to predict if each target sample belongs to either one of the knwon classes or to an unknown class, 
being rejected in the latter case.
We evaluate the method on the Office-Home benchmark \cite{OfficeHomeDataset} using a new OSDA metric.

@@

Here ${\bf v_i}$ is the output of the penultimate layer of $R_1$,
$\gamma({\bf z}_i)$ is the centroid of the features associated to class $i$
(notice that the centroid is relative to a different rotation class $i$ in the multi-head variant),
$||\cdot||_2^2$ is the $l$-2 norm and $\lambda$ is the weight associated with the center loss term.
The additional center loss contribution should favor the learning of hidden features which have
a smaller intra-class variance, resulting in a more discriminative representation
when combined with the standard cross-entropy loss,
which in contrast tries to enlarge the distance between the means of the classes.

>>>>

The approach presented in this paper combines the power of the self-supervised learning with the standard supervised learning approach for semantic class recognition.
We propose a two stage method aiming to identify and isolate unknown class samples in the first stage, 
and reducing the domain gap between domains in the second stage to avoid negative transfer.
A schematic view of the stages can be seen in figures \ref{fig:step1}, \ref{fig:separation}, \ref{fig:step2}.
This is done by using a modified version of the rotation task as self-supervised method,
predicting the relative rotation between an image and its rotated version.
Finally, a classifier is used to predict if each target sample belongs to either one of the knwon classes or to an unknown class, 
being rejected in the latter case.
We evaluate the method on the Office-Home benchmark \cite{OfficeHomeDataset} using a new OSDA metric.

@@

Here ${\bf v_i}$ is the output of the penultimate layer of $R_1$,
$\gamma({\bf z}_i)$ is the centroid of the features associated to class $i$
(notice that the centroid is relative to a different rotation class $i$ in the multi-head variant),
$||\cdot||_2^2$ is the $l$-2 norm and $\lambda$ is the weight associated with the center loss term.
The additional center loss contribution should favor having hidden features which have
a smaller intra-class variance, resulting in a more discriminative representation
when combined with the standard cross-entropy loss,
which in contrast tries to enlarge the distance between the means of the classes.
